---
title: "Groove Research Findings"
author: "Qi Draaisma"
date: "10-2-2021"
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    theme: simplex
---


Findings Storyboard
========================
```{r echo=FALSE, message=FALSE, results=FALSE, warnings=FALSE}

# Cleaning the Data and retrieving only the fully finished responses.

library(ggplot2)
library(gridExtra)
library(plotly)
library(tidyverse)
library(dplyr)

GDat <- read.csv("Groove_Data.csv")
vars <- c("Not at all", "Not that much", "Not really", "Somewhat", "A lot", "Very much")

counts <- as.data.frame(bind_rows(
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q9_1) %>% rename("Answer" = Q9_1) %>% mutate(aspect = "pb", sample = 1, duration = "long"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q19_1) %>% rename("Answer" = Q19_1) %>% mutate(aspect = "pb", sample = 2, duration = "short"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q22_1) %>% rename("Answer" = Q22_1) %>% mutate(aspect = "pb", sample = 3, duration = "long"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q25_1) %>% rename("Answer" = Q25_1) %>% mutate(aspect = "pb", sample = 4, duration = "short"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q28_1) %>% rename("Answer" = Q28_1) %>% mutate(aspect = "pb", sample = 5, duration = "long"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q31_1) %>% rename("Answer" = Q31_1) %>% mutate(aspect = "pb", sample = 6, duration = "short"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q34_1) %>% rename("Answer" = Q34_1) %>% mutate(aspect = "pb", sample = 7, duration = "long"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q37_1) %>% rename("Answer" = Q37_1) %>% mutate(aspect = "pb", sample = 8, duration = "short"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q40_1) %>% rename("Answer" = Q40_1) %>% mutate(aspect = "pb", sample = 9, duration = "long"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q43_1) %>% rename("Answer" = Q43_1) %>% mutate(aspect = "pb", sample = 10, duration = "short"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q46_1) %>% rename("Answer" = Q46_1) %>% mutate(aspect = "pb", sample = 11, duration = "long"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q49_1) %>% rename("Answer" = Q49_1) %>% mutate(aspect = "pb", sample = 12, duration = "short"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q52_1) %>% rename("Answer" = Q52_1) %>% mutate(aspect = "pb", sample = 13, duration = "long"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q55_1) %>% rename("Answer" = Q55_1) %>% mutate(aspect = "pb", sample = 14, duration = "short"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q58_1) %>% rename("Answer" = Q58_1) %>% mutate(aspect = "pb", sample = 15, duration = "long"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q61_1) %>% rename("Answer" = Q61_1) %>% mutate(aspect = "pb", sample = 16, duration = "short"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q64_1) %>% rename("Answer" = Q64_1) %>% mutate(aspect = "pb", sample = 17, duration = "long"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q67_1) %>% rename("Answer" = Q67_1) %>% mutate(aspect = "pb", sample = 18, duration = "short"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q9_2) %>% rename("Answer" = Q9_2) %>% mutate(aspect = "utm", sample = 1, duration ="long"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q19_2) %>% rename("Answer" = Q19_2) %>% mutate(aspect = "utm", sample = 2, duration ="short"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q22_2) %>% rename("Answer" = Q22_2) %>% mutate(aspect = "utm", sample = 3, duration ="long"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q25_2) %>% rename("Answer" = Q25_2) %>% mutate(aspect = "utm", sample = 4, duration ="short"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q28_2) %>% rename("Answer" = Q28_2) %>% mutate(aspect = "utm", sample = 5, duration ="long"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q31_2) %>% rename("Answer" = Q31_2) %>% mutate(aspect = "utm", sample = 6, duration ="short"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q34_2) %>% rename("Answer" = Q34_2) %>% mutate(aspect = "utm", sample = 7, duration ="long"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q37_2) %>% rename("Answer" = Q37_2) %>% mutate(aspect = "utm", sample = 8, duration ="short"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q40_2) %>% rename("Answer" = Q40_2) %>% mutate(aspect = "utm", sample = 9, duration ="long"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q43_2) %>% rename("Answer" = Q43_2) %>% mutate(aspect = "utm", sample = 10, duration = "short"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q46_2) %>% rename("Answer" = Q46_2) %>% mutate(aspect = "utm", sample = 11, duration = "long"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q49_2) %>% rename("Answer" = Q49_2) %>% mutate(aspect = "utm", sample = 12, duration = "short"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q52_2) %>% rename("Answer" = Q52_2) %>% mutate(aspect = "utm", sample = 13, duration = "long"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q55_2) %>% rename("Answer" = Q55_2) %>% mutate(aspect = "utm", sample = 14, duration = "short"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q58_2) %>% rename("Answer" = Q58_2) %>% mutate(aspect = "utm", sample = 15, duration = "long"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q61_2) %>% rename("Answer" = Q61_2) %>% mutate(aspect = "utm", sample = 16, duration = "short"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q64_2) %>% rename("Answer" = Q64_2) %>% mutate(aspect = "utm", sample = 17, duration = "long"),
  count(GDat[which(GDat$Q19_2 != "" & GDat$RecipientEmail == "" & GDat$Q46_2 != "" & GDat$Q31_2 != "" & GDat$Q58_2 != ""),], Q67_2) %>% rename("Answer" = Q67_2) %>% mutate(aspect = "utm", sample = 18, duration = "short")
))

'%notin%' <- function(x, y)!('%in%'(x,y))

for (x in unique(counts$sample)){
  for (a in unique(counts$aspect)){
      for (var in vars) {
        if (var %notin% unique(counts[which(counts$sample == x & counts$aspect == a), "Answer"])) {
          d <- unique(counts[which(counts$sample == x), "duration"])
          counts[nrow(counts) + 1,] = c(var, 0, a, x, d)
        }
    }
  }
}

counts$n <- as.numeric(counts$n)
```

This Storyboard will help me with organizing my data and ultimately present it to Makiko.

It will also help me organize my brain while keeping up with making nice-looking plots and data.

Happy me!

The Data
=======================
### A Roster with the full data of every sample at once

```{r}
counts %>%
  ggplot(
    aes(
      x = Answer,
      y = n,
      fill = aspect
      )
    ) +
  geom_bar(stat="identity", position=position_dodge()) +
  facet_wrap(~as.numeric(sample), ncol = 4, nrow=6)
```
***
* Very unorganized
* Helps with recognizing trends
* A very exploratory plot :)

It seems the initial hypothesis is wrong! Hooray!

The second hypothesis that was created during the reviewing of the samples did seem to work out!

Changes seem to be minimal!

Melody 1
========================



```{r fig.width=14, fig.height=10}
S1 <- counts %>%
  filter(sample == 1) %>%
  ggplot(
    aes(
      x = Answer,
      y = n,
      fill = aspect, n
      )
    ) +
  geom_bar(stat="identity", position="dodge") +
  ggtitle("Melody 1, Horns, Long") +
  geom_text(
    aes(
      label = n
    ),
    position=position_dodge(0.9),
    vjust=2
  )

S1b <- counts %>%
  filter(sample == 2) %>%
  ggplot(
    aes(
      x = Answer,
      y = n,
      fill = aspect, n
    )) +
  geom_bar(stat="identity", position="dodge") +
  ggtitle("Melody 1, Horns, Short") +
  geom_text(
    aes(
      label = n
    ),
    position=position_dodge(0.9),
    vjust=2
  )

S2 <- counts %>%
  filter(sample == 3) %>%
  ggplot(
    aes(
      x = Answer,
      y = n,
      fill = aspect
      )
    ) +
  geom_bar(stat="identity", position=position_dodge()) +
  ggtitle("Melody 1, Piano, Long") +
  geom_text(
    aes(
      label = n
    ),
    position=position_dodge(0.9),
    vjust=2
  )

S2b <- counts %>%
  filter(sample == 3) %>%
  ggplot(
    aes(
      x = Answer,
      y = n,
      fill = aspect
      )
    ) +
  geom_bar(stat="identity", position=position_dodge()) +
  ggtitle("Melody 1, Piano, Short") +
  geom_text(
    aes(
      label = n
    ),
    position=position_dodge(0.9),
    vjust=2
  )

S3 <- counts %>%
  filter(sample == 5) %>%
  ggplot(
    aes(
      x = Answer,
      y = n,
      fill = aspect,
      )
    ) +
  geom_bar(stat="identity", position=position_dodge()) +
  ggtitle("Melody 1, Sitar, Long") +
  geom_text(
    aes(
      label = n
    ),
    position=position_dodge(0.9),
    vjust=2
  )

S3b <- counts %>%
  filter(sample == 6) %>%
  ggplot(
    aes(
      x = Answer,
      y = n,
      fill = aspect,
      )
    ) +
  geom_bar(stat="identity", position=position_dodge()) +
  ggtitle("Melody 1, Sitar, Short") +
  geom_text(
    aes(
      label = n
    ),
    position=position_dodge(0.9),
    vjust=2
  )


grid.arrange(S1, S1b, S2, S2b, S3, S3b)
```

Melody 2
=======================

```{r fig.width=14, fig.height=10}
S4 <- counts %>%
  filter(sample == 7) %>%
  ggplot(
    aes(
      x = Answer,
      y = n,
      fill = aspect, n
      )
    ) +
  geom_bar(stat="identity", position="dodge") +
  ggtitle("Melody 2, Horns, Long") +
  geom_text(
    aes(
      label = n
    ),
    position=position_dodge(0.9),
    vjust=2
  )

S4b <- counts %>%
  filter(sample == 8) %>%
  ggplot(
    aes(
      x = Answer,
      y = n,
      fill = aspect, n
      )
    ) +
  geom_bar(stat="identity", position="dodge") +
  ggtitle("Melody 2, Horns, Short") +
  geom_text(
    aes(
      label = n
    ),
    position=position_dodge(0.9),
    vjust=2
  )

S5 <- counts %>%
  filter(sample == 9) %>%
  ggplot(
    aes(
      x = Answer,
      y = n,
      fill = aspect
      )
    ) +
  geom_bar(stat="identity", position=position_dodge()) +
  ggtitle("Melody 2, Piano, Long") +
  geom_text(
    aes(
      label = n
    ),
    position=position_dodge(0.9),
    vjust=2
  )

S5b <- counts %>%
  filter(sample == 10) %>%
  ggplot(
    aes(
      x = Answer,
      y = n,
      fill = aspect
      )
    ) +
  geom_bar(stat="identity", position=position_dodge()) +
  ggtitle("Melody 2, Piano, Short") +
  geom_text(
    aes(
      label = n
    ),
    position=position_dodge(0.9),
    vjust=2
  )

S6 <- counts %>%
  filter(sample == 11) %>%
  ggplot(
    aes(
      x = Answer,
      y = n,
      fill = aspect,
      )
    ) +
  geom_bar(stat="identity", position=position_dodge()) +
  ggtitle("Melody 2, Sitar, Long") +
  geom_text(
    aes(
      label = n
    ),
    position=position_dodge(0.9),
    vjust=2
  )

S6b <- counts %>%
  filter(sample == 12) %>%
  ggplot(
    aes(
      x = Answer,
      y = n,
      fill = aspect,
      )
    ) +
  geom_bar(stat="identity", position=position_dodge()) +
  ggtitle("Melody 2, Sitar, Short") +
  geom_text(
    aes(
      label = n
    ),
    position=position_dodge(0.9),
    vjust=2
  )


grid.arrange(S4, S4b, S5, S5b, S6, S6b)
```

Melody 3
=======================

```{r fig.width=14, fig.height=10}
S7 <- counts %>%
  filter(sample == 13) %>%
  ggplot(
    aes(
      x = Answer,
      y = n,
      fill = aspect, n
      )
    ) +
  geom_bar(stat="identity", position="dodge") +
  ggtitle("Melody 3, Horns, Long") +
  geom_text(
    aes(
      label = n
    ),
    position=position_dodge(0.9),
    vjust=2
  )

S7b <- counts %>%
  filter(sample == 14) %>%
  ggplot(
    aes(
      x = Answer,
      y = n,
      fill = aspect, n
      )
    ) +
  geom_bar(stat="identity", position="dodge") +
  ggtitle("Melody 3, Horns, Short") +
  geom_text(
    aes(
      label = n
    ),
    position=position_dodge(0.9),
    vjust=2
  )

S8 <- counts %>%
  filter(sample == 15) %>%
  ggplot(
    aes(
      x = Answer,
      y = n,
      fill = aspect
      )
    ) +
  geom_bar(stat="identity", position=position_dodge()) +
  ggtitle("Melody 3, Piano, Long") +
  geom_text(
    aes(
      label = n
    ),
    position=position_dodge(0.9),
    vjust=2
  )

S8b <- counts %>%
  filter(sample == 16) %>%
  ggplot(
    aes(
      x = Answer,
      y = n,
      fill = aspect
      )
    ) +
  geom_bar(stat="identity", position=position_dodge()) +
  ggtitle("Melody 3, Piano, Short") +
  geom_text(
    aes(
      label = n
    ),
    position=position_dodge(0.9),
    vjust=2
  )

S9 <- counts %>%
  filter(sample == 17) %>%
  ggplot(
    aes(
      x = Answer,
      y = n,
      fill = aspect,
      )
    ) +
  geom_bar(stat="identity", position=position_dodge()) +
  ggtitle("Melody 3, Sitar, Long") +
  geom_text(
    aes(
      label = n
    ),
    position=position_dodge(0.9),
    vjust=2
  )

S9b <- counts %>%
  filter(sample == 18) %>%
  ggplot(
    aes(
      x = Answer,
      y = n,
      fill = aspect,
      )
    ) +
  geom_bar(stat="identity", position=position_dodge()) +
  ggtitle("Melody 3, Sitar, Short") +
  geom_text(
    aes(
      label = n
    ),
    position=position_dodge(0.9),
    vjust=2
  )


grid.arrange(S7, S7b, S8, S8b, S9, S9b)
```


Differences through note length
==================================

```{r}
diff <- data.frame(Answer=as.character(),
                   d=as.numeric(),
                   sample=as.numeric(),
                   aspect=as.character(),
                   color=as.character())



for (x in 1:9){
  for (ap in unique(counts$aspect)) {
  for (var in vars) {
    d <- as.numeric(counts[which(counts$sample == x & counts$Answer == var & counts$aspect == ap), "n"]) - as.numeric(counts[which(counts$sample == x + 1 & counts$Answer == var & counts$aspect == ap), "n"])
    
    c = ifelse(ap == "utm", "rgb(255, 0, 0)", "rgb(0, 128, 0)")
    
    diff[nrow(diff) + 1,] <- c(var, d, x, ap, c)
  }
  }
}

p1 <- plot_ly(data = diff%>%filter(sample == 1), x = ~Answer, y = ~as.numeric(d), type = "bar", color=~aspect, showlegend=F)
p2 <- plot_ly(data = diff%>%filter(sample == 2), x = ~Answer, y = ~as.numeric(d), type = "bar", color=~aspect, showlegend=F)
p3 <- plot_ly(data = diff%>%filter(sample == 3), x = ~Answer, y = ~as.numeric(d), type = "bar", color=~aspect, showlegend=F)
p4 <- plot_ly(data = diff%>%filter(sample == 4), x = ~Answer, y = ~as.numeric(d), type = "bar", color=~aspect, showlegend=F)
p5 <- plot_ly(data = diff%>%filter(sample == 5), x = ~Answer, y = ~as.numeric(d), type = "bar", color=~aspect)
p6 <- plot_ly(data = diff%>%filter(sample == 6), x = ~Answer, y = ~as.numeric(d), type = "bar", color=~aspect, showlegend=F)
p7 <- plot_ly(data = diff%>%filter(sample == 7), x = ~Answer, y = ~as.numeric(d), type = "bar", color=~aspect, showlegend=F)
p8 <- plot_ly(data = diff%>%filter(sample == 8), x = ~Answer, y = ~as.numeric(d), type = "bar", color=~aspect, showlegend=F)
p9 <- plot_ly(data = diff%>%filter(sample == 9), x = ~Answer, y = ~as.numeric(d), type = "bar", color=~aspect, showlegend=F)

subplot(p1, p2, p3, p4, p5, p6, p7, p8, p9, nrows=4, shareY=T, shareX=T)
```

Differences for M1
================

```{r}
subplot(p1, p2, p3)
```

Differences for M2
================

```{r}
subplot(p4, p5, p6)
```

Differences for M3
================

```{r}
subplot(p7, p8, p9)
```
